`traveltime`: an R package to calculate walking and motorised travel time from user locations

### 2025-01-24 paper/paper.qmd
added missing ORCIDs to paper resolve #34 resolve #35 that was easy der brain

---
title: "`traveltime`: an R package to calculate walking and motorised travel time from user locations"
format:
  md: default
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags: 
  - R
  - geographic information systems
  - spatial analysis
authors:
  - name: Gerard E Ryan
    orcid: 0000-0000-0000-0000
    corresponding: true
    affiliation: "1, 2"
  - name: Nick Tierney
    orcid: 1234
    affiliation: "1, 3"
  - name: Nick Golding
    orcid: 1234
    affiliation: "1, 3 "
  - name: Daniel Weiss
    orcid: 1234
    affiliation: "1, 3"
affiliations:
 - name: The Kids Research Institute Australia, Nedlands 6009 WA, Australia
   index: 1
 - name: Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
   index: 2
 - name: Curtin University, Bentley, WA, Australia
   index: 3
date: In prep 2025
bibliography: paper.bib
---

>>>>

---
title: "`traveltime`: an R package to calculate walking and motorised travel time from user locations"
format:
  #md: default
  html:
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags: 
  - R
  - geographic information systems
  - spatial analysis
authors:
  - name: Gerard E Ryan
    orcid: 0000-0003-0183-7630
    corresponding: true
    affiliation: "1, 2"
  - name: Nick Tierney
    orcid: 0000-0003-1460-8722
    affiliation: "1, 3"
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: "1, 3 "
  - name: Daniel Weiss
    orcid: 0000-0002-6175-5648
    affiliation: "1, 3"
affiliations:
 - name: The Kids Research Institute Australia, Nedlands 6009 WA, Australia
   index: 1
 - name: Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
   index: 2
 - name: Curtin University, Bentley, WA, Australia
   index: 3
date: In prep 2025
bibliography: paper.bib
---
